%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------
\documentclass[a4paper,11pt]{article}

%----------------------------------------------------------------------------------------
%	FONT
%----------------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0.098, 0.109, 0.173}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}

%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{\textbf{Duy Nguyen}} \\[7.5pt]
\Large{\textbf{Frontend Software Intern}} \\[7.5pt]
\href{https://github.com/thanhduy1706}{\normalsize\raisebox{-0.05\height}\faGithub\ thanhduy1706} \ $|$ \ 
\href{https://www.linkedin.com/in/thanhduy1706/}{\normalsize\raisebox{-0.05\height}\faLinkedin\ thanhduy1706} \ $|$ \
\href{https://tduy1706.vercel.app/}{\normalsize\raisebox{-0.05\height}\faGlobe \ Portfolio} \ $|$ \ 
\href{mailto:ndtduy.work@gmail.com}{\normalsize\raisebox{-0.05\height}\faEnvelope \ ndtduy.work@gmail.com} \ $|$ \ 
\href{tel:+84986404189}{\normalsize\raisebox{-0.05\height}\faMobile \ (+84) 986 404 189} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------

%Interests/ Keywords/ Summary
% \section{Summary}
% This CV can also be automatically complied with and published using GitHub Actions. For details, \href{https://github.com/jitinnair1/autoCV}{click here}.

% \begin{tabularx}{\linewidth}{ @{}l r@{} }
% \textbf{Designation} & \hfill Mar 2019 - Jan 2021 \\[3.75pt]
% \multicolumn{2}{@{}X@{}}{
% \begin{minipage}[t]{\linewidth}
%     \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
%         \item[--] long long line of blah blah that will wrap when the table fills the column width
%         \item[--] again, long long line of blah blah that will wrap when the table fills the column width but this time even more long long line of blah blah. again, long long line of blah blah that will wrap when the table fills the column width but this time even more long long line of blah blah
%     \end{itemize}
%     \end{minipage}
% }
% \end{tabularx}

%Projects
\section{Projects}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{IntelliSpace | Frontend Developer} & \hfill \textbf{Feb 2024 - Present}\\[3.75pt]
\multicolumn{2}{@{}X@{}}{
    \begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
        \item \textbf{Tech stack:} React.JS (Next.JS), TailwindCSS, Framer Motion, Java Springboot on Azure.
        \item \textbf{Responsibility:} I specialize in creating user-centric web experiences. Design intuitive interfaces, translate them into clean user interface code, and build reusable components using React.JS.  To protect data and guide users, I implement comprehensive input validation and volatile memory such as Redux Toolkit.  Finally, I integrate dynamic functionality by efficiently fetching and managing data from APIs with Axios.
        \item \textbf{Description:} User can create various folders in the workspace, upload files, and photos to store to cloud. Users can create live chat with teammates and live communication via video meetings.
        \item \textbf{Achievement:} Architected and implemented a web application workspace featuring a robust server configuration, scalable cloud infrastructure, and intuitive, responsive UX/UI design.
        \item \href{https://github.com/thanhduy1706/IntelliSpace}{\faGithub\ github.com/thanhduy1706/IntelliSpace}
    \end{itemize}
    \end{minipage}
    }
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{DataVizX | Frontend Developer} & \hfill  \textbf{Sep 2023 – Dec 2023}\\[3.75pt]
\multicolumn{2}{@{}X@{}}{
    \begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
        \item \textbf{Tech stack:} React.JS, Chart.JS, TailwindCSS, Node.JS, Express.JS on Vercel.
        \item \textbf{Responsibility:} My expertise lies in creating user-friendly web interfaces. This includes designing for optimal usability, coding UIs with precision, and developing modular components for efficiency. I safeguard user data and provide clear guidance through robust data validation.  I also ensure seamless functionality by expertly integrating frontends with APIs by using Axios.
        \item \textbf{Description:} Implement front-end components for chart manipulation (creation, updates, deletion) accessible after user authentication. Design a note-taking module and set up the UI to facilitate conversations with an AI support system.
        \item \textbf{Achievement:} To build an effective data-driven web app, use Chart.js for dynamic visualizations. Emphasize a user-friendly experience with a clear interface and informative labeling.  Make sure your app adapts seamlessly to different devices with responsive design, allowing users to explore your data visualizations on any screen size.
        \item \href{https://github.com/thanhduy1706/DataVizX}{\faGithub\ github.com/thanhduy1706/DataVizX}
    \end{itemize}
    \end{minipage}
    }
\end{tabularx}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{@{}l X@{}}	
2021 - present & Bachelor of Network Engineering in Information Technology \hfill\break at \textbf{International University VNU-HCMC}
\end{tabularx}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------
\section{Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
Programming skills: &  \normalsize{JavaScript, HTML/CSS, Java, C/C++}\\
Front-end skills:  &  \normalsize{React.JS, Next.JS, TailwindCSS, User Responsive Design}\\
Other skills:  & 
\begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
        \item Working Process: Agile, Scrum.
        \item Teamwork Tool: Trello, Jira.
        \item Design: Figma, Adobe Illustrator, Adobe Photoshop.
        \item Basic knowledge of version control systems (e.g., Git).
        \item Microsoft Office.
    \end{itemize}\\  
Language:  &  \normalsize{English.}\\
\end{tabularx}

\vfill
\center{\footnotesize Last updated: \today}

\end{document}
